### 2023-12-03 thesis/chapters/02-analysis-B-features.tex
Come up with layout of summarization tables for best features

Multiple subsets of predictors produced by each evaluation metric can train several variants of a classification model. Sets of attributes can be likewise combined into an ensemble by majority voting, taking the best features out of every group.

>>>>

Multiple subsets of predictors produced by each evaluation metric can train several variants of a classification model. Sets of attributes can be combined into an ensemble by \emph{electoral system}. One such example is \textbf{majority voting} which chooses the best feature out of the group. \textbf{Rank product} unifies several feature orderings by computing the geometric mean of feature rank in every experiment realization~\cite{breitling_rank_2004}.

### 2023-12-03 thesis/chapters/03-design.tex
Come up with layout of summarization tables for best features

	- calcultate euclidian measure of feature 
	- correlation point biserial, fisher, mutual information
		- Sperman rank correlation: corr, f_stat, 1.000000
	- calculate feature rank
		- Temporal (A) - Remove corr: pp, skewness, margin
			pp	1.442250
			std	2.080084
			max	2.714418
			rms	3.174802
			skewness	6.082202
			margin	6.868285

>>>>

	- calcultate euclidian measure of feature 
	- correlation point biserial, fisher, mutual information
		- Sperman rank correlation: corr, f\_stat, 0.98
	- calculate feature rank
		- Temporal (A) - Remove corr: pp, skewness, margin
			shape 	1.442250
			std 	1.587401
			rms 	2.620741
			max 	4.308869
			pp 	5.428835
			skewness 	5.646216

			std 	1.000000
			rms 	2.000000
			pp 	3.000000
			max 	4.000000
			skewness 	5.593445
